
%%% A template to produce a nice-looking Curriculum Vitae.
%%% Adapted from Kieran Healy
%%% Most recent version is at http://kjhealy.github.com/kjh-vita
%%%
%%% ------------------------------------------------------------------------
%%% Requirements that are included in a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%%
%%%
%%%
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip,
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}
\usepackage{geometry}
 \geometry{
 a4paper }
\usepackage{org-preamble-xelatex}
\usepackage{fontawesome5,url}
\usepackage{enumitem} %get rid of spaces in listed


%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Omoju Miller}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myemail{omoju@fimio.xyz}
\def\myweb{omojumiller.com}
\def\mytwitter{@omojumiller}
\def\mylinkedin{linkedin.com/in/omojumiller}
\def\mygithub{github.com/omoju}
\def\myversion{}
\def\myrevision{}


%% \def\myaffiliation{Duke University}
\def\myauthor{Omoju Thomas Miller}
\date{} % not used (revision control instead)
\def\mykeywords{Omoju, Thomas Miller, Omoju Thomas Miller, Vita, CV, Resume, Founder}

%%%------------------------------------------------------------------------
%%% Git version tracking
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
%% \input{vc}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe.
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\setromanfont[Mapping={tex-text},
	          Numbers={OldStyle},
	          Ligatures={Common}]{Minion Pro}
\setsansfont[Mapping=tex-text,
	         Ligatures={Common}, 
	         Colour=AA0000]{Unit-Medium}
\setmonofont[Mapping={tex-text},
             Scale={0.72}]{Hack} 

\newfontface\scheader[SmallCapsFont={Minion Pro},SmallCapsFeatures={Letters=SmallCaps}]{Minion Pro}

\newfontface\addressblock[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~}

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the vc
% package---see docs for vc package for details. Comment out this line
% if you're not using vc, and also remove the \input{vc} line above.
\pagestyle{kjh}
\thispagestyle{kjhgit}


%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}

\end{minipage}
\hfill
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{2in}
  \flushright \footnotesize  \addressblock
  {\scriptsize  \texttt{\href{http://twitter.com/omojumiller}{\mytwitter}} \, \faTwitter }  \\
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
  {\scriptsize  \texttt{\href{\mylinkedin}{\mylinkedin}} \, \faLinkedin} \\
  {\scriptsize  \texttt{\href{\mygithub}{\mygithub}} \, \faGithub} \\
  {\scriptsize  \texttt{\href{\myweb}{\myweb}} \, \faGlobe}
\end{minipage}

\medskip

%% Name 
\noindent{\HUGE\scheader \textsc{\href{http://omojumiller.com/portfolio/}{omoju thomas miller}}}

\bigskip       
\noindent{\large\scheader \textsc{Ex-Google | White House Influencer | UC Berkeley Ph.D.}}
\reversemarginpar



%% Professional Experience
\marginhead{\sffamily {\vskip 0.35em} profession \newline experience}
\medskip

\ind {\large \textbf{Fimio} - \textit{Founder and CEO}} \hfill Oakland, CA | June 2022-Present
\begin{itemize}[nolistsep]
\item[-] Bringing trust to the trustless web.
\end{itemize} 

\ind {\large \textbf{GitHub} - \textit{Technical Advisor to CEO}} \hfill San Francisco, CA | Feb 2020-Feb 2021
\begin{itemize}[nolistsep]
\item[-]Led Technical Research and Tiger Team projects..
\item[-]Provided technical input, working with product teams to understand and define technical
issues, brief the executive, leadership team and stakeholders as needed.
\end{itemize} 

\ind {\large \textbf{GitHub} - \textit{Senior Data Scientist, Machine Learning}} \hfill San Francisco, CA | July 2017-Present
\begin{itemize}[nolistsep]
\item[-]Works on applied machine learning to optimize software development lifecycle on GitHub.
\item[-]Co-Developed Discovery Dashboard Recommendation Engine.
\item[-]Attained a click-through rate of 20\%.
\end{itemize} 

\ind {\large \textbf{Insight Data Science} - \textit{Data Science Fellow}} \hfill Palo Alto, CA | Jan 2017-Jun 2017
\begin{itemize}[nolistsep]
\item[-]Built a large-scale hierarchical classification model for a YC backed management service company.
\item[-]Scaled solution to accommodate growing taxonomy of item categories.
\end{itemize} 

\ind {\large \textbf{UC Berkeley} - \textit{CSEd Doctoral Candidate}} \hfill Berkeley, CA | Dec 2013-May 2016
\begin{itemize}[noitemsep,nolistsep]
\item[-] Designed a machine learning, research study to investigate gender in intro CS.
\item[-] Developed a data science unit within a historical \href{http://www.whitehouse.gov/the-press-office/2014/12/08/fact-sheet-new-commitments-support-computer-science-education}{intro CS course}, CS10.
\end{itemize}

\ind {\large \textbf{Google} - \textit{Technology Portfolio Manager}} \hfill Mountain View, CA | Feb 2014-Dec 2015
\begin{itemize}[nolistsep]
\item[-]Co-led a \$15M CSEd portfolio. Grew the portfolio by 25\%.
\item[-]Co-led the development of vocabulary glossary for Android Development course.
\end{itemize} 

\ind {\large \textbf{ICSI\footnote{International Computer Science Institute}} - \textit{Graduate Researcher}} \hfill Berkeley, CA | Mar 2011-Dec 2012
\begin{itemize}[nolistsep]
\item[-] Built a conceptual metaphor \href{http://metaphor.icsi.berkeley.edu}{Semantic Wiki} capable of ingesting data in English, and Farsi.
\item[-] Contributed to the design of conceptual metaphor framework.
\end{itemize} 

\ind {\large \textbf{UniversityNow} - \textit{Data Scientist (Intern)}} \hfill San Francisco, CA | Jun 2012 -Aug 2012
\begin{itemize}[nolistsep]
\item[-]Led a 3 person team responsible for creating an analytics console.
\item[-]Pulled and integrated data from two separate database management systems.
\end{itemize} 

\ind {\large \textbf{TEDxEuclidAve} - \textit{Founder and Curator}} \hfill Berkeley, CA | Aug 2011-Aug 2012
\begin{itemize}[noitemsep,nolistsep]
\item[-]Led a 10 person team responsible for executing on the vision.
\item[-]Led strategy for \href{http://www.ted.com/tedx/events/3790}{TEDx}EuclidAve, a 100+ member conference, bringing together innovative thinkers across technology, design and entertainment in service of social entrepreneurship.
\end{itemize}

\ind {\large \textbf{Center for Advanced Sensors} - \textit{Graduate Researcher}} \hfill Memphis, TN | Aug 2003-Nov 2006
\begin{itemize}[nolistsep]
\item[-]Co-designed \href{https://scholar.google.com/scholar?hl=en&q=Building+a+Sensor+Ontology\%3A+A+Practical+Approach+Leveraging+ISO+and+OGC+Models.&btnG=&as_sdt=1\%2C43&as_sdtp=}{OntoSensor}, a sensor ontology using Semantic Web Ontology Language (OWL).
\item[-]Built an intelligent reasoning agent capable of reasoning with data in XML and RDF formats
\end{itemize}

\ind {\large \textbf{Thoughtware Learning Technologies} - \textit{Software Engr}} \hfill Memphis, TN | Aug 1999-Nov 2001
\begin{itemize}[nolistsep]
\item[-]Contributed to the development of an AI eLearning workforce development platform.
\item[-]Quality assurance for an eLearning management system.
\end{itemize} 

\bigskip



%% Education
\marginhead{\sffamily {{\vskip -0.23em} education}}

\ind \textbf{UC Berkeley} - Computer Science Education, Ph.D. \hfill 2016

\ind \textbf{University of Memphis} - Electrical and Computer Engineering, M.S. \hfill 2004

\ind \textbf{University of Memphis} - Computer Science, B.S. \hfill 2001

\bigskip

%% Teaching Experience
\marginhead{\sffamily {\vskip 0.35em} teaching \newline experience}
\medskip

\ind {\large \textbf{Metis Data Science} - \textit{Instructor}} \hfill San Francisco, CA | Fall 2017
\begin{itemize}[noitemsep,nolistsep]
\item[-] Introduction to Data Science
\end{itemize}

\ind {\large \textbf{UC Berkeley} - \textit{Graduate Student Instructor}} \hfill Berkeley, CA | Spring 2013
\begin{itemize}[noitemsep,nolistsep] 
\item[-] Introduction to Cognitive Science
\end{itemize} 

\ind {\large \textbf{UC Berkeley} - \textit{Graduate Student Instructor}} \hfill Berkeley, CA | Spring 2011
\begin{itemize}[noitemsep,nolistsep] 
\item[-] Introduction to C++ programming
\end{itemize} 

\ind {\large \textbf{University of Memphis} - \textit{Adjunct Faculty}} \hfill Memphis, TN | Spring 2010
\begin{itemize}[noitemsep,nolistsep]
\item[-] C programming for Engineers
\end{itemize}

\ind {\large \textbf{University of Memphis} - \textit{Graduate Student Instructor}} \hfill Memphis, TN | Spring 2006
\begin{itemize}[noitemsep,nolistsep]
\item[-] Computer Software Engineering
\end{itemize}

\ind {\large \textbf{University of Memphis} - \textit{Graduate Student Instructor}} \hfill Memphis, TN | Spring 2005
\begin{itemize}[noitemsep,nolistsep]
\item[-] Data Visualization
\end{itemize}

\ind {\large \textbf{University of Memphis} - \textit{Graduate Student Instructor}} \hfill Memphis, TN | Spring 2004
\begin{itemize}[noitemsep,nolistsep]
\item[-] Introduction to Computer Engineer Lab
\end{itemize}

\bigskip 


%% Publications
\marginhead{\sffamily {\vskip 0.35em} publications}
\medskip

\noindent\emph{Conference proceedings \vspace{0.05in}}

%% Use revnumerate environment if numbered publications are needed.
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind Omoju Miller. 2016. ``Gaining Insights into the Effects of Culturally Responsive Curriculum on Historically Underrepresented Students' Desire for Computer Science.'' \emph{Proceedings of the 123rd ASEE Annual Conference, New Orleans, LA.}

\ind D.J. Russomanno, C. Kothari and O. Thomas. 2005. ``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=E7z_wrwAAAAJ&sortby=pubdate&citation_for_view=E7z_wrwAAAAJ:u5HHmVD_uO8C}{Building a Sensor Ontology: A Practical Approach Leveraging ISO and OGC Models}.'' \emph{The 2005 International Conference on Artificial Intelligence, Las Vegas, NV} 637--643.

\ind D.J. Russomanno, C. Kothari and O. Thomas. 2005. ``\href{http://scholar.google.com/citations?view_op=view_citation&hl=en&user=E7z_wrwAAAAJ&citation_for_view=E7z_wrwAAAAJ:u-x6o8ySG0sC}{Sensor Ontologies: From Shallow to Deep Models.}'' \emph{Proceedings of the 37th Southeastern Symposium on Systems Theory, IEEE Press, Tuskegee, AL} 107--112.

\ind O. Thomas and D.J. Russomanno. 2005. ``\href{http://scholar.google.com/citations?view_op=view_citation&hl=en&user=E7z_wrwAAAAJ&citation_for_view=E7z_wrwAAAAJ:d1gkVwhDpl0C}{Applying the Semantic Web Expert System Shell to Sensor Fusion using Dempster-Shafer Theory.}'' \emph{Proceedings of the 37th Southeastern Symposium on Systems Theory, IEEE Press, Tuskegee, AL}. 11--14.

\ind O.A. Thomas and D.J. Russomanno. 2004. ``\href{http://scholar.google.com/citations?view_op=view_citation&hl=en&user=E7z_wrwAAAAJ&citation_for_view=E7z_wrwAAAAJ:2osOgNQ5qMEC}{SWEXSYS: A Semantic Web Expert System Shell}.'' \emph{Proceedings of the IASTED International Conference on Artificial Intelligence and Applications, part of the 23rd Multi-Conference on Applied Informatics, Innsbruck, Austria} 240--245.

\bigskip

\noindent\emph{Workshops and Presentations  \vspace{0.05in}}

%\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
%\begin{revnumerate}

\ind Omoju Miller. 2017. ``An introduction to Bagging Models.'' \emph{Demystifying Deep Learning and AI, Noroff, Oslo.}

\ind Jennifer Arguello, Tiffany Price, Alexis Martin, Frieda McAlear, Omoju Miller, Dan Garcia. 2015. ``Engaging Underrepresented Youth in Computer Science."  \emph{Computer Science Teachers Association (CSTA) in Grapevine, TX.}

\ind Omoju Miller. 2015. ``Towards a Global Framework for Culturally Resonant Learning.'' \emph{2015 Sage Assembly in Paris, France.}

\ind Omoju Miller and Oluwole Solana. 2014. ``From San Francisco to Johannesburg, introducing girls to Computer Science in Industry supported programs.'' \emph{2014 Grace Hopper Conference in Pheonix, AZ.}

\ind Daniel D Garcia, Brian Harvey, Tiffany Barnes, Dan Armendariz, Jon McKinsey, Zachary MacHardy, Omoju Miller, Barry Peddycord III, Eugene Lemon, Sean Morris, Josh Paley. 2014. ``\href{http://dl.acm.org/citation.cfm?id=2539026}{AP CS Principles and the Beauty and Joy of Computing Curriculum.'' }\emph{Proceedings of the 45th ACM Technical Symposium on Computer Science Education,} 746--746.

\ind Brian Harvey, Daniel D Garcia, Tiffany Barnes, Nathaniel Titterton, Omoju Miller, Dan Armendariz, Jon McKinsey, Zachary Machardy, Eugene Lemon, Sean Morris, Josh Paley. 2014. ``\href{http://dl.acm.org/citation.cfm?id=2539022}{Snap!(Build your own Blocks).''} \emph{Proceedings of the 45th ACM Technical Symposium on Computer Science Education,} 749--749.

\ind Omoju Miller, Jordan Arnesen, Eric Chu, Grayson Flood, Kevin Funkhouser, Alex Greenspan, Daniel Hsu. 2013. ``Hiphopathy: A Computational Thinking Process to Encourage Empathy.'' \emph{2013 California Cognitive Science Conference, Berkeley, CA.}

%\end{revnumerate}
%\newpage
\bigskip
\noindent\emph{Essays and reviews \vspace{0.05in}}

%\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
%\begin{revnumerate}


\ind Frieda McAlear, Omoju Miller, Dan Garcia, Alexis Martin. 2016. ``\href{http://www.csta.acm.org/Communications/sub/CSTAVoice_Files/csta_voice_01_2016.pdf}{Equity in Computer Science: From Exposure to Entrepreneurship.''} \emph{Computer Science Teacher's Association (CSTA) Voice, } 9--10.

\ind Omoju Miller. 2014. ``\href{http://dl.acm.org/citation.cfm?id=2604994}{Its Deeper than Rap, Toward Culturally Responsive CS.'' }\emph{XRDS: Crossroads,  The ACM Magazine for Students, } 28--30.

\ind Omoju Miller. 2013. ``\href{http://kaporcenter.org/wp-content/uploads/2013/10/Kapor_CodingLandscape_R3.pdf}{Winning with Both Sides of the Coin.''} \emph{Coding Nation Report} 6--7.
% %\end{revnumerate}

 \bigskip

%\newpage

\marginhead{\sffamily {\vskip 0.5em}selected \newline conference \newline presentations \newline since 2012}
\medskip

\ind Keynote, ``\href{https://www.youtube.com/watch?v=JShvXcL66NQ}{Cognitive Apprenticeship - Experience in Open Source}, Linux Conference Australia - Linux.conf.au, January, 2021.

\ind Speaker, ``\href{https://www.youtube.com/watch?v=JHS9yQMUzb0}{Science in the Age of Data: Accelerating Human Progress}." JupyterCon, October, 2020.

\ind Keynote, ``\href{https://www.youtube.com/watch?v=uC5ZRaK8Ebc}{Africa - The Next Frontier}." DLD Munich, Munich, January, 2020.

\ind Speaker, ``\href{https://www.oreilly.com/library/view/oreilly-tensorflow-world/0636920333111/video328051.html}{Why is machine learning seeing exponential growth in its communities?}" O'Reilly TensorFlow World, Santa Clara, October, 2019.

\ind Speaker, ``\href{https://www.youtube.com/watch?v=NPk-y_tH7JY}{AI at the Frontier: A Global Viewpoint}." Fortune Brainstorm Tech, July, 2019.

\ind Keynote, ``\href{https://youtu.be/Teq3pa1L7Tg}{A new vision for the global brain: Deep learning with people instead of machines}." O'Reilly Velocity Conf, London, October 2018.

\ind Speaker, ``\href{https://www.youtube.com/watch?v=vB5nTx5fUXM}{Opening Keynote - GitHub Universe}." GitHub Universe, San Francisco, October 2018.


\ind Speaker, ``Building Data Products at GitHub." Pluralsight Live, Utah, August 2018.

\ind Fireside Chat, Nairobi Women in Machine Learning. Nairobi, Kenya, June 2018.

\ind Presenter, ``\href{http://proceedings.mlr.press/v81/ekstrand18b/ekstrand18b.pdf}{All The Cool Kids, How Do They Fit In? Popularity and Demographic Biases in Recommender Evaluation and Effectiveness}." Papers We Love - San Francisco, California, April 2018. 

\ind Keynote panelist ``\href{https://youtu.be/_F534KBWFJc}{Data Science: Past, Present, Future }.'' DataEngConf, California, April 2018.

\ind Speaker ``\href{https://youtu.be/BFWVHSeakkg}{On learning AI: The Myth of Innate Ability in Tech}.'' TEDxSanFrancisco, California, October 2017.

\ind Speaker ``On learning AI: The myth of innate ability in tech.'' Data Institute, California, October 2017.

\ind Panelist ``Black Work, Black Wealth, Black Futures." Data For Black Lives, MIT, Massachusetts, November 2017.

\ind Speaker ``What Makes a Coder.'' Etsy, New York, February 2017.

\ind Panelist ``Moral Machines: How Philosophy can help AI Decide Right from Wrong." Grace Hopper Celebration of Women in Computing, Texas, October 2016.

\ind Keynote ``15+ Years of Learning Computational Intelligence.'' Annual OUSD Dinner with a Scientist, California, May 2016.

\ind Panelist ``SPIE Women in Optics.'' SPIE Photonics West Annual Conference, California, February 2016.

\ind Speaker ``Breaking Barriers: Changing the Landscape.'' Andela, Lagos, Nigeria, January 2016.

\ind Panelist ``Behind the Click: Intersection of Women of Color in STEM and Social Justice.'' Black Girls Code, California, December 2015.

\ind Keynote ``Moonshot Thinking.'' Joint Board of Advisors Meeting, Purdue School of Engineering and Technology, IUPUI, Indiana, October 2015.

\ind Keynote ``Breaking Barriers: Changing the Landscape.'' Youth Start Up Weekend at Castlemont High School, California, May 2015.

\ind Speaker, ``Breaking Barriers: Changing the Landscape.'' Office of Institutional Diversity, Harvey Mudd College, California, December 2014.

\ind Keynote, ``\href{https://www.youtube.com/watch?v=owXez6sIRbY&ab_channel=IUCEWIT}{Inventing the Mythical Creature: Or How to Stay, Lead, and Delight in Tech as a Woman.}'' Annual Celebration of the IU Center of Excellence for Women in Technology (CEWiT), Indiana, October 2014.

\ind Speaker, ``Made With Code.'' Annual Dreamforce Developer's Conference, Callifornia, October 2014.

\ind Speaker, ``Inventing the Mythical Creature: Or How to Stay, Lead, and Delight in Tech as a Woman.'' Focus 100, New York, September 2014.

\ind Presenter, ``\#ThisIsGrit.'' \textbf{White House} Department of Education EdDataPalooza, Washington DC, January 2014.

\ind Speaker, ``Unintended Bias." Departmental Heads Gathering, \textbf{White House}, Washington DC, February 2013.

\ind Panelist, ``Social Justice in the Age of Big Data.'' Swinging and Flowing: Inclusion and Diversity in the Age of Data. The Data and Democracy Initiative @ CITRIS Berkeley, Berkeley, April 2012.

\bigskip

\marginhead{\sffamily {\vskip 0.6em}grants,\newline honors, \newline \& awards}
\medskip

\ind Member (Expert Network: AI), World Economic Forum, Davos, Switzerland, March 2017.

\ind Bloomberg Beta Future Founder, Bloomberg Beta, California, 2014.

\ind Winner, White House Dept of Edu EdDataPalooza, Washington DC, January 2014

\ind Kapor Capital Fellows, California, 2012.

\ind SESAME Graduate Division Fellowship, UC Berkeley, 2010--2011

\ind Herff College of Engineering fellowship, Memphis, 2002--2006.

\bigskip

\marginhead{\sffamily {\vskip 0.6em}press,\newline podcast, \newline \& coverage}
\medskip

\ind \textbf{The Business Journal}, \href{https://www.bizjournals.com/sanfrancisco/inno/stories/awards/2023/01/13/startups-to-watch.html}{Startups to Watch: Fimio wants to help you trust crypto and Web3}. January, 2023.

\ind \textbf{TWIML Podcast}, \#313,  \href{https://twimlai.com/podcast/twimlai/machine-learning-github-omoju-miller/}{Machine Learning at GitHub with Omoju Miller}. October, 2019.

\ind \textbf{DeepLearning.AI}, \href{https://www.deeplearning.ai/blog/working-ai-at-the-office-with-senior-mle-omoju-miller/}{Working AI: At the Office with Senior MLE Omoju Miller}. August, 2019.


\ind \textbf{Fortune}, \href{https://fortune.com/2019/07/17/africa-is-techs-next-great-frontier-github-ai/}{Africa Is Tech’s Next Great Frontier, Github A.I. Expert Says}. July, 2019.

\ind \textbf{Venture Beat}, \href{https://venturebeat.com/ai/github-wants-ai-to-help-developers-code/}{GitHub wants AI to help developers code}. October, 2018.

\ind \textbf{Harvard Business Review}, \href{https://hbr.org/2018/08/what-data-scientists-really-do-according-to-35-data-scientists}{What Data Scientists Really Do, According to 35 Data Scientists}. August, 2018.

\ind \textbf{DataFramed Podcast}, \#29, \href{https://www.datacamp.com/community/podcast/machine-learning-github}{Machine Learning \& Data Science at Github (with Omoju Miller)}. July, 2018.

\ind \textbf{The Observer}, \href{http://observer.com/2017/02/omoju-miller-etsy-stem-pipeline/}{Berkeley PhD's 4-Step Plan to a STEM Pipeline That Works for Everyone}. February 16, 2017.

\ind \textbf{Stack Overflow Podcast }, \#91, \href{https://soundcloud.com/stack-exchange/stack-overflow-podcast-91-can-you-stump-nick-craver}{Can You Stump Nick Craver?}. October 2016.

\ind \textbf{Science with Tom parody rap video}, \href{https://www.youtube.com/watch?v=q5mmE05e82I&ab_channel=ScienceWithTom}{Everybody's Got Questions (Yup)}. May 2016.

\ind \textbf{JavaScript Air Podcast}, \href{http://audio.javascriptair.com/e/022-jsair-the-science-of-people-in-tech-with-kate-edwards-omoju-miller-and-steve-andrews/}{The Science of People in Tech}. May, 2016.

\ind \textbf{HBCU to Startup Podcast}, \href{https://www.youtube.com/watch?v=T0wQRr4RuqM&ab_channel=HBCUtoStartup}{Learners Guild, Investing in You to Code}. March, 2016.

\ind \textbf{The Hanselman Minutes Podcast: Fresh Air for Developers}, \href{http://hanselminutes.com/488/redesigning-computer-science-101-education-with-omoju-miller}{Redesigning Computer Science 101 Education with Omoju Miller}. August, 2015.

\ind \textbf{Pivot TV}, \href{http://roadtripnation.com/leader/omoju-miller}{RoadTrip Nation: Omoju's Open Road}. March, 2015.

\ind \textbf{\#BITTechTalk}, \href{https://www.blacksintechnology.net/the-road-to-50-podcast-african-americans-on-the-role-of-higher-education-in-innovation/}{African Americans on the role of Higher Education in Innovation}. December, 2014.

\ind \textbf{NPR's  All Tech Considered}, \href{http://www.npr.org/sections/alltechconsidered/2014/10/05/351851015/fortune-tellers-step-aside-big-data-looks-for-future-entrepreneurs}{Fortune-Tellers, Step Aside: Big Data Looks For Future Entrepreneurs}.October 5, 2014.

\ind \textbf{Berkeley Bytes}, \href{http://best.berkeley.edu/2015/03/11/best-labber-in-berkeley-byte-qa-with-cs-ed-reformer-and-phd-candidate-omoju-miller/}{Q\&A with CS Ed Reformer and PhD Candidate Omoju Miller}. March 11, 2014.

\end{document}
